---
title: "Simulating Insurance Claims"

author:
  - name: Krishna Kumar Shrestha 
date: "`r Sys.Date()`"
output: distill::distill_article
---

```{css, echo=FALSE}
   
h1 {
  color: black;
  text-align: center;
}
h2 {
  color: blues9;
  text-align: center;
}
p {
  font-family: verdana;
  font-size: 16px;
  font-weight: bold;
}

table {
  width: 100%;
}

```

```{r setup, include=FALSE}
knitr::opts_chunk$set(
	echo = TRUE,
	message = FALSE,
	warning = FALSE
)
```

# Introduction

R is very good tool for simulation. In this small blog post , i will show a basic code on how we can perform simulation of insurance claims.

## 1. Problem and Assumption

Before we execute any R code, we need to make assumption of the problem. Lets discuss it step by step. 

1. lets consider that we are writing 1000 identical insurance policies next year

2.  We want to measure the losses we expect to pay on claims resulting from these policies. Lets assume that there is 10% chance that a single policy having claim.

3.  we will use discrete probability distribution (Poisson distribution ) to simulate the frequency

4.  then we will need to simulate loss amount for each claim. For this we will use log normal distribution with a log mean of 9 and a log standard deviation of 1.75.

In real world probability of single policy having claim and distribution to be used is determined by actuary .

## 2.Single frequency and severity observation

for reproducing same simulation lets set the seed

```{r}
set.seed(101)
```

now lets generate a single frequency from the poisson distribution.

```{r}
lamda<- 1000*0.1
freq<- rpois(n=1,lambda = lamda)
freq
```

Now lets generate a seventies. Each severity represent the ultimate value of 1 claim.

```{r}
s<- rlnorm(n=freq,meanlog = 9,sdlog = 1.75)
s
```

In the above example our frequency was 96 and by summing the severities of these 96 claims we arrive at the observation total of 7493485

## 3.Run for many obesrvation

Above we learned how to run a single observations. by inspecting the results of many observations we can determine the confidence level of experiencing different loss amount.

lets assume the number of observation this time be 1000.

```{r}
n<-1000

```

Generating frequncy

```{r}

freq<-rpois(n=n,lambda = lamda)

```

G**enerating Seventies**

```{r}
obs<-purrr::map(freq,function(freq)rlnorm(n=freq,meanlog = 9,sdlog = 1.75))
```

**Presenting in table**

```{r}
library(dplyr)
i<-0
obs<- purrr::map(obs,function(sev){
  i=i+1
  data.frame(
    ob=i,
    sev=sev
  )
})

obs<- dplyr::bind_rows(obs)
kableExtra::kbl(head(obs,5))



```

## 4.Inspection of results

### Plot the distribution of observation

```{r}

library(ggplot2)

obs %>%
  ggplot()+
  aes(sev)+
  geom_histogram()

```

### View summary

```{r}

summary(obs$sev)

```

# Conclusion

**Simulations allow you to answer highly complicated questions that would be impossible to solve directly from math equations and probability density function.**
