---
title: "Using dplyr"

author:
  - name: Krishna Kumar Shrestha
    
date: "`r Sys.Date()`"
output: distill::distill_article
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(
	echo = TRUE,
	message = FALSE,
	warning = FALSE
)

```

# How to use dplyr

> To install the package, write

> install.packages("dplyr")

**After the package has been installed, you have to load it with the following command**

```{r}
library(dplyr)
```

**The main commands of the dplyr package are:**

1.  **select()**: choosing a subset of columns

2.  **filter()**: choosing a subset of rows

3.  **arrange()**: sort the rows

4.  **mutate()**: add new columns

5.  **summarise()**: aggregates the values

6.  **group\_by()**: change the data into grouped data in order to apply functions to each of the groups separately

**Next we will show you some simple examples to demonstrate the functionality of dplyr package.**

# **lets take a data set first.For this example i have taken storms data set .**

```{r}
data("storms")
head(storms)
```

1.  <div>

    # **select(): how to use**

    </div>

**lets assume that we want name,year,month,and day column form the storm data set. this can be done using select()**

```{r}
data1<-storms %>%
  select(name,year,month,day)
head(data1)
```

2.  <div>

    # filter(): How to use it?

    </div>

**lets assume that we want name,year,month=12,and day column form the storm data set. this can be done using select() and filter()**

```{r}
data2<- storms %>%
  select(name,year,month,day) %>%
  filter(month==12)
head(data2)

```

3.  <div>

    # arrange(): How to use it

    </div>

**lets assume that we want name,year,month=12,and day column form the storm data set and arrange it in ascending order of year,day . this can be done using select() ,filter() and arrange**

```{r}
data3<-storms %>%
  select(name,year,month,day) %>%
  filter(month==12) %>%
  arrange(year,day)
head(data3)
```

4.  <div>

    # mutate(): How to use it?

    </div>

**lets assume that we want name,year,month=12,and day column form the storm data set and create new column with month-1**

```{r}
data4<- storms %>%
  select(name,year,month,day) %>%
  filter(month==12) %>%
  mutate(new_month=month-1)
head(data4)
```

5.  <div>

    # group\_by() and summarize(): how to use?

    </div>

**lets assume that we want mean pressure every year. this can be done using group\_by() and Summarize()**

```{r}
data5<- storms %>%
  group_by(year) %>%
  summarise(mean_pressure=mean(pressure,na.rm = T))
head(data5)
```
